\svnidlong
{$HeadURL:  $}
{$LastChangedDate:  $}
{$LastChangedRevision:  $}
{$LastChangedBy:  $}
\chapter[Introduction]{Introduction}
%\chapter[Origins of Philosphy]{Introduction\versionfootnote}
%\label{cha:dddd}
\label{cha:introduction}
\section{The Why of philosphy?} 
How the trials of reason brought us philosphy.
What is philosphy? Why it existed? and Why it is important? How is philosphy is being used today in today's technological world.
Should we enforce the preception of science from the prespective of philosphy? 

\subsection{The crafting of philopshy}
Man precives his surroundings, man aims to interfer play with his surroundings, man imagine how he can extend this ability to affect his surroundings, man realize that he can't go as far as he can imagine. Man starts to make tools to help him closer and closer to realize his iamginations.

In a way philosphy is a tool that Man uses to develop his intellect, to expand his knowledge and to attain wisdom that makes him far more capable to "play". In a way that mainfists the story of man's existance.

but who created philosphy? and even though it is evidant that such a tool to develop intellect is needed, Why it was set to be philosphy and not any other kind of science?? why not mathematics? why not coloring? why not anything else? In other words why we use philosphy to precieve other sciences and not vice-versa? 10pages.

\subsection{The Fallacy of a Univesal Philosphy}
Ancient cultures, what do we know about ancient cultures? what do we know about the origins of sciences?
ancient greek, ancient chinese, ancient 
islamic philosphy, buddist philosphy, Go philosphy?

doctorian of philopshy, ppl say thesis as they are wise enough to know that nothing is real and nothing is solid, and each got its own opinon which may or may deliver success in ones lifetime.

\subsection{Philosphy and technology}
technology is also a tool for man to expand his intellect, precivied from the prespective of philosphy, technology conferms with the solid foundations of idealism created by plato.



\section{the idea of plato's philosphy and idealism} 10pages
Gottfried Wilhelm Leibniz use the term idealism to refer to plato's philosphy.

\section{software from the prespective of plato idealism} 10pages

\section{prespectives and patterns, patterns of usability and usability of patterns.} 10pages

\section{software architecutre, design, algorithm, etc as patterns encapsulated in levels of granularity} 10pages

\section{Philosphy is the way we manage to collect our consiouse methods of thinking under a terminology family that represent ideas.}

\section{understanding datastructures and algorithims is important for developing well-crafted software.}

Having a good understanding of data structures and algorithms is an important part of developing well-crafted software. Software engineering is a broad subject, but a great deal can be gleaned from a few concepts. There are concepts that appear to reacurrue at diffrent levels of granriuality. Such a pattern is evident insoftware engineering practices.

modularity



Domain-specific frameworks are (defenition), exisited for a long time now. Software developers (engineers) are often customed to the use of an encapsulating object that mainifests a reusability of some sort, such as a software library or a software framework. domain-specific frameworks

% need to do 
% svn propset svn:keywords "URL Date Revision Author" introduction.tex
% for version information to work

% content goes here

% below: for emacs. 
% source specials allows switching between emacs and xdvi.
% get rid of the source-specials line for final version

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "thesis"
%%% TeX-source-specials-mode: on
%%% End:
